---
title: "Social Networks Final"
author: "Larri Miller"
date: "5/8/2021"
output: html_document
---

---
title: "Larri Networks Final"
output: html_notebook
---
```{r}
tweets <- read.csv("SharpieGate.csv")
```

Using network analysis methods that I learned in Wayne Xu's "Digital Behavioral Data" class-- figured it was easier because it's catered to tweets specifically
```{r}
install.packages("devtools")
install.packages("graphTweets")
library(devtools) 
devtools::install_bitbucket("JohnCoene/twinetverse")
library(graphTweets)
library(twinetverse)
```

```{r}
extractrt <- function(tweets){
  rt <- tweets %>% 
    gt_edges(screen_name, retweet_screen_name) %>% # get edges
    gt_nodes() %>% # get nodes
    gt_collect() # collect
  
  return(rt)
}
rtnet <- extractrt(tweets)
extractmt <- function(tweets){
  
  mt <- tweets %>% 
    gt_edges(screen_name, mentions_screen_name) %>% # get edges
    gt_nodes() %>% # get nodes
    gt_collect() # collect
  
  return(mt)
}
mtnet <- extractmt(tweets)
#define a function called nodes to extract node information from a network object
nodes <- function(net){
  
  c(edges, nodes) %<-% net
  nodes$id <- as.factor(nodes$nodes) 
  nodes$size <- nodes$n 
  nodes <- nodes2sg(nodes)
  nodes <- nodes[,2:5]
  
  return(nodes)
}
#define a function called edges to extract edge information from a network object
edges <- function(net){
  
  c(edges, nodes) %<-% net
  edges$id <- seq(1, nrow(edges))
  edges <- edges2sg(edges)
  
  return(edges)
}
#apply the two self-defined functions
rtnet_nodes <- nodes(rtnet)
rtnet_edges <- edges(rtnet)
mtnet_nodes <- nodes(mtnet)
mtnet_edges <- edges(mtnet)
```

```{r}
nodes_unique <- unique(rtnet_nodes)
```

Converting to igraph, creating "net" as the network object
```{r}
library(igraph)

net <- graph_from_data_frame(d=rtnet_edges, vertices = nodes_unique, directed = T)
```


Now following Week 7's tutorial for the power law distribution:
```{r}
install.packages(c("devtools", "network", "sna", "igraph", "intergraph"))
library(devtools)
install_github("DougLuke/UserNetR")

library(igraph)
library(UserNetR)
```

Gonna plot out the degree distribution
```{r}
plot(degree.distribution(net), type = "b",
     xlab = "Degree",
     ylab = "Proportion",
     main = "SharpieGate Tweet Network")

plot(degree.distribution(net),log='xy', 
     xlab="Degree",
     ylab="Proportion") 
```
# make unique lsit of nodes
Well that looks hideous

-- look at degree, cutoff
-- log distribution

Summary stats of network, just to warmup
```{r}
summary(net)

graph.density(net)

mean(degree(net))

transitivity(net)

```

trying to isolate nodes with degree 7
```{r}
OL <- which(degree(net) >= 7)
length(OL)
OL
```

I've got 53 influencers in this network with a degree of over 7. Cool. 

Trying to add a binary variable 
```{r}
net <- net %>%
  mutate(influencer = ifelse((degree(net) >= 7), 1, 0))
```
Okay I can't add a new colunm to an igraph object that way...

Let's change this to a network object bc I like working with those better
```{r}
library("intergraph")
class(net)
network=asNetwork(net)
class(network)
```

```{r}
summary(network)
gden(network)
components(network)

lgc <- component.largest(network,result = "graph")
gd <-geodist(lgc)
max(gd$gdist)

gtrans(network, mode="graph")

deg=degree(network, gmode="digraph",cmode="freeman")
outdeg=degree(network,gmode="digraph",cmode="outdegree")
indeg=degree(network,gmode="digraph",cmode="indegree")
summary(deg)
summary(outdeg)
summary(indeg)
hist(deg)
hist(outdeg)
hist(indeg)


# plot
op <- par(mar=c(0,0,0,0)) 
gplot(network, displayisolates = F, main = "Network")
```
proportion of reciprocated ties -- or how many people retweet each other
```{r}
grecip(network, measure="edgewise") 
(2*dyad.census(network)[,"Mut"]/network.edgecount(network))
```

Let's make a subgraph of influencers
```{r}
netInfluencers <- get.inducedSubgraph(network, which(degree(network) >= 7))
class(netInfluencers)

netRest <- get.inducedSubgraph(network, which(degree(network) < 6))

IRecip <- grecip(netInfluencers, measure="edgewise") 
(2*dyad.census(netInfluencers)[,"Mut"]/network.edgecount(netInfluencers))
IRecip

rRecip <- grecip(netRest, measure="edgewise") 
(2*dyad.census(netRest)[,"Mut"]/network.edgecount(netRest))
rRecip
```

Let's try some visualization
```{r}
idlabel <- get.vertex.attribute(netInfluencers,"id")
idlabel
par(op)
gplot(netInfluencers, usearrows = TRUE, vertex.col="violet", gmode="graph", label = idlabel)

network.size(netInfluencers)
summary(netInfluencers)
```
let's try to vary node size
```{r}

par(op)

gplot(netInfluencers, usearrows = TRUE, vertex.col="violet", gmode="graph",mode="fruchtermanreingold", label = idlabel)

gplot(netInfluencers, usearrows = TRUE, vertex.col="violet", gmode="graph",mode="circle", vertex.cex=1.5, label = idlabel)

gplot(netInfluencers, usearrows = TRUE, vertex.col="violet", gmode="graph",mode="princoord", vertex.cex=1.5, label = idlabel)

```


```{r}
gplot(netRest, usearrows = TRUE, vertex.col="grey", gmode="graph")
```
```{r}
library(sna)
summary(netInfluencers)
gden(netInfluencers)
components(netInfluencers)

lgc <- component.largest(netInfluencers,result = "graph")
gd <-geodist(lgc)
max(gd$gdist)

gtrans(netInfluencers, mode="graph")
```

hmmmm whole network plot with varying node sizes?
```{r}
deg = degree(network, gmode="graph")

par(op)
gplot(network,usearrows=F,vertex.cex=deg/35)
```

